---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# jasco2

__Warning: This package is still under development !__

A package for easy Spectrophotometer data handling.

## Installation

You can install the released version of jasco2 from GitHub.

```{r installation, eval = FALSE}
# should not work, since the repo is private
devtools::install_github("mirkko-hub/jasco2")
```

## Example

Easy data handling of Jasco spectrophotometer (JASCO Corp., V-560, Rev. 1.00) files - you only need three things:

* __data__ _(.txt output from spectrophotometer)_
* __design__ _(record of individual files and grouping information + optional flagging for removal, notes)_
* __treatmemt__ _(additional information specifying the different groups)_


##### Import files

```{r}
library(tidyverse, warn.conflicts = FALSE)
library(magrittr, warn.conflicts = FALSE)
library(jasco2)
```


_Given a bunch of .txt files from Jasco Spec,_
```{r import_1, echo = TRUE}
files <- system.file("extdata", paste0(1:28, ".txt") , package = "jasco2", mustWork = TRUE)
head(files)
```

_... some design tibble,_
```{r import_2, echo = TRUE}
design <- readr::read_csv(system.file("extdata", "design.csv", package = "jasco2", mustWork = TRUE))
head(design)
```
_... and and a treatment tibble,_
```{r import_3, echo = TRUE}
treatment <- readr::read_csv(system.file("extdata", "treatment.csv", package = "jasco2", mustWork = TRUE))
head(treatment)
```

_we can easily combine all information in a tidy tibble, that facilitates further analysis!_
```{r tibble, echo = TRUE}
df <- jasco_tibble(filenames = files, design, treatment, rmflag = FALSE, rmblank = TRUE)
head(df)
```



##### Process data

In the given example, we performed an enzyme coupled ATP hydrolysis assay.
So we measured NADH oxidation (the consumption of NADH is recorded at 340 nm) as a response to ATP hydrolysis via the depicted reaction -
each oxidized NADH molecule reports the hydrolysis of one molecule of ATP.

Let's say we want to calculate turnover rates of the ATPase of interest.
All we need to do is:

* convert absorbance units into concentration
* apply a linear model (with customized interval, response and predictor variables)
* extract the slopes (estimates) for all reaction
* and convert these into turnover rates

_(with optional summary by specified groups)_

__like so:__

```{r process}
data <- df %>%
  convert_absorbance(., "NADH") %>%
  jasco_extract_lm(., response = NADH, predictor = Time_s, min = 75, max = 175)
head(data)
  
params <- data %>%
  jasco_extract_params(., .bgcorr = FALSE, .protein_uM = 6, .unit = "sec", .factor = -1, Group)
head(params$data)
head(params$summary)
```

##### Plot data

```{r plot_lm}
ggplot() +
  geom_point(data = data %>% unnest(data) %>% filter(., Label != "Control"),
             mapping = aes(x = Time_s, y = NADH), size = 0.1) +
  geom_path(data = data %>% unnest(augment) %>% filter(., Label != "Control"),
            mapping = aes(x = Time_s, y = .fitted, group = Exp_ID), colour = "green") +
  facet_grid(Label ~ Protein) +
  theme_classic()
```


```{r plot_turnover}
ggplot() +
  geom_boxplot(data = params$data %>% filter(Label != "Control"), aes(x = Label, y = turnover, colour = Protein)) +
  geom_point(data = params$data %>% filter(Label != "Control"), aes(x = Label, y = turnover, colour = Protein)) +
  facet_grid(. ~ Protein) +
  ggsci::scale_color_npg() +
  theme_classic()
```
